Data Recovery and Pulse Position Modulation with a Photon Number Resolving SNSPD

### 2023-08-22 manuscript.tex
overleaf update

\begin{abstract*}

\end{abstract*}

%%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Abstract}

Photon number resolution is an emerging capability of advanced Superconducting Nanowire Single Photon Detectors. If leveraged to it's full potential, PNR capabilty can have a profound impact on the usefulness of SNSPDs is certain quantum applications including linear optical quantum computing, quantum networks, and quantum sensing. Discrimination of not just the number of photons in an optical pulse but also pulse arrival time with high accuracy is an open problem, complicated by the nuanced way in which these two degrees of freedom are intertwined in the response function of these detectors. In this work we put a differential readout SNSPD to the ultimate test. We test it's capabilities in a Pulse Position Modulation experiment whereby data is sent in the arrival time of optical pulses derived from a 20 GHz optical clock. We show the detector is capable of discriminating the arrival time of photons to 50~ps wide bins with high accuracy while simultaneously providing photon number information about the impinging optical pulses. We find that a careful statistical analysis of the PNR response is necessary to back-out a precise measurement of pulse arrival time.

\section{Introduction}

@@

\subsection{Pulse Position Modulation for Deep Space Communication}

@@

\subsection{Development of a modulation source}

@@

\section{Methods}

>>>>

\begin{abstract*} 
Photon number resolution is an emerging capability of advanced Superconducting Nanowire Single Photon Detectors. If leveraged to it's full potential, PNR capabilty can have a profound impact on the usefulness of SNSPDs is certain quantum applications including linear optical quantum computing, quantum networks, and quantum sensing. Discrimination of not just the number of photons in an optical pulse but also pulse arrival time with high accuracy is an open problem, complicated by the nuanced way in which these two degrees of freedom are intertwined in the response function of these detectors. In this work we put a differential readout SNSPD to the ultimate test. We test it's capabilities in a Pulse Position Modulation experiment whereby data is sent in the arrival time of optical pulses derived from a 20~GHz optical clock. We show the detector is capable of discriminating the arrival time of photons to 50~ps wide bins with high accuracy while simultaneously providing photon number information about the impinging optical pulses. We find that a careful statistical analysis of the PNR response is necessary to back-out a precise measurement of pulse arrival time.
\end{abstract*}

%%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{pulse-position-modulation-for-deep-space-communication}{%
\subsection{Pulse Position Modulation for Deep Space Communication}\label{pulse-position-modulation-for-deep-space-communication}}

@@

\hypertarget{development-of-a-modulation-source}{%
\subsection{Development of a modulation source}\label{development-of-a-modulation-source}}

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}
